\section{Problems and Requirements of Chemical Protective Clothing}

Scenarios where workers are exposed to hazardous materials require chemical protective clothing (CPC). These tasks are extremely demanding—both physically and mentally—particularly because of the equipment. Since Type 1 suits are not gas-permeable, they compromise the body's ability to regulate temperature, leading to exhaustion and heat fatigue even faster [\cite{holmerProtectiveClothingHot2006}]. The exertion is exacerbated by heavier equipment and heat stress, ultimately reducing work capacity [\cite{smolanderCardiorespiratoryThermalEffects1984}]. Maximum working time in a full-body suit with self-contained breathing apparatus (SCBA) is therefore limited and might decrease even more depending on air and exhaustion levels.

Further, the material and shape of the suit limit mobility, the field of view, and muffle hearing, intensified by additional noise, e.g., from the SCBA. Even trained personnel might need double the time to complete tasks when wearing CPC [\cite{murrayEffectsChemicalProtective2011}].

Physiological parameters measurable in regular work conditions for catching heat exhaustion early include heart rate [\cite{adamsModelProtectiveClothing1994}].

Other environmental hazards include electricity and possible explosive atmospheres.
- elimination not in task scope, but to be avoided

Task environments can be summarized into two extremes. First, a controlled space with either bright or poor lighting and simple backgrounds. Second, a scenario like an emergency response, in which most variables are unknown. It is likely that backgrounds will be varied and lighting conditions can change.

The types of information needed would differ by task, but life-sustaining paramaters should be front and center in all of them.

users are/will be trained with equipment -> able to forego certain design principles

is there a distinction between end user and professional/trained user?
shneiderman (user interfaces): novice + expert user, universal usability

would therorize acceptance of HUD is better with newly trained people with regards to mental load, since they don't need to change existing patterns

currently, movements are grouped: manometer is checked when getting arm out of sleeve for radio comms anyway

an AR-HUD could be a solution to keep equipment handling to the minimum needed for the actual task, keep the worker's hands free and heighten situational awareness by supplying relevant information
SA is improved directly (relevant information at a glance) and indirectly (alleviating mental load which can be reallocated)

---

\cite{adamsModelProtectiveClothing1994}

collects + summarizes relevant effects, cite secondary?

CPC impacts performance by causing heat stress, limited range-of-motion, reduced efficiency

\cite{smolanderCardiorespiratoryThermalEffects1984}

oxygen consumption + HR higher in PPE

heart rate similar behavior, 21\% 80-120; 41\% 120-170 bpm

consumption increase to a steadily rising level 
(warning when sudden rise/fall outside of norm)

\cite{murrayEffectsChemicalProtective2011}

wearing CPC significantly increases task completion time

has some design recommendations, but more for interaction, not relevant for HUDs