\section{Attention Management}

% habituation: less attention to any stimulus that occurs frequently

%There are two ways in which an object can be focused: bottom-up and top-down. 
Bottom-up attention occurs subconsciously, triggered by outside stimuli. In the top-down process, the brain directs the eyes toward a consciously selected object. Interestingly, top-down attention lessens the effect of distracting stimuli when concentrating on a target [\cite{connorVisualAttentionBottomUp2004}].

When multiple stimuli compete for attention, even salient targets might be ignored if they are irrelevant to the current goal. This is referred to as inattentional blindness [\cite{jensenChangeBlindnessInattentional2011}]. \textcite{caterSelectiveQualityRendering2002} leverages this effect to only render parts of frames in high-quality around the current fixation point.

\subsection{Situation Awareness}

The concept of situation awareness provides context for the visualizations.
% to estimate the requirements for efficient information acquisition in dynamic situations
% "Acquiring and maintaining SA becomes increasingly difficult, however, as the complexity and dynamics of the environment increase"
% "In complex and dynamic environments, attention demands resulting from information overload, complex decision making, and multiple tasks can quickly exceed a person's limited attention capacity"

Making good judgements becomes increasingly difficult when performing demanding procedures while trying to maintain awareness of the surrounding area. The risks associated with these activities prohibit human error, further increasing stress levels.
\textcite{endsleyTheorySituationAwareness1995} highlights the role of situation awareness as a foundation for good decision-making in dynamic situations. She outlines three levels of SA, namely perception, comprehension and projection, of which perception is the most significant for UI design. 
This stage requires collecting the information relevant to the situation. In level 2 this information will be analyzed to form "a holistic picture of the environment, comprehending the significance of objects and events." Finally, likely outcomes can be determined by understanding the dynamics of the situation.

It is evident that situation awareness is therefore dependent on the processes of attention described in section \ref{sec:HVS_attention}. Subsequently, this illustrates the necessity of a thorough understanding of the pieces required for achieving good situation awareness to design a well-functioning HUD. The amount of information that can be rapidly and accurately obtained is directly influenced by how it is presented. In addition to prioritizing and organizing that information around task objectives, \textcite{endsleyTheorySituationAwareness1995} mentions the advantage of systems providing processed information rather than the data it is based on (e.g. displaying remaining time based on current oxygen amount and usage). 

Special attention should be paid to reserve highly salient features to critical events that truly necessitate changing the course of action. Further, it is vital to maintain a balance between showing all relevant information, while simultaneously avoiding visual overload. While looking for inaccessible information, other important content may be overlooked. Conversely, "filtering of extraneous information (not related to SA needs) and reduction of data (by processing and integrating low-level data to arrive at SA requirements)" is necessary to prevent clutter. This reiterates the importance of accurately evaluating and prioritizing task-relevant information.

Considering these recommendations supports evaluating the interaction of all components, since emphasizing some elements inevitably comes at the expense of others. Assessing the design concept by the amount of situation awareness it provides serves as the last step of ensuring the effectiveness of the system.

% "Cognitive load theory (CLT) is concerned with the design of interfaces that allow users maximize their working memory when problem solving. This includes eliminating any subjective mental load that may be imposed by the instruction interface." DABOR 2019 SIMULT INTERPRETATION

\subsection{Peripheral Displays and Glanceability}

A peripheral display keeps information related to a primary task available.
On the other hand, so-called notification displays are meant to prompt action, actually interrupting the user. A peripheral display offers the choice of whether or not to continue the current action [\cite{matthewsDefiningDesigningEvaluating2005}].

Glanceable information means it can be comprehended quickly and easily once it is paid attention to [\cite{matthewsDesigningGlanceablePeripheral2006}].
% - "Glanceability is critical to peripheral display design because users need to quickly glance at and read displayed information with minimal interruption to their primary task."

% ACHIEVING GLANCEABILITY
% - "Visuals that support top-down search will be easy to cognitively interpret. Visuals that support bottom-up search enable relevant information to pop-out. \cite{baldassiPopoutTargetsModulated2004}"
%   - "Pop-out is a bottom-up drawing of attention to an object, which occurs when an object within the visual field is distinctive along some visual dimension (for example, possessing a distinctive color or brightness when compared with other objects in the field)." -> POWER OF CONTRAST

% - "If visual features are to be used successfully in glanceable displays, they will need to balance distinctiveness with too much demand for attention."
% - variables were used to distinguish between versions of otherwise the same items (e.g. email categories of notifications)

% \cite{birnholtzAwarenessDesktopExploring2010} peripheral displays

Glanceability is directly impacted by the displayed amount of items, their salience, etc.—i.e. the attentional limits described in section \ref{sec:HVS_attention}.
% by the displayed "amount and type of information [\cite{matthewsDesigningGlanceablePeripheral2006}], .

Interpreting a display of one piece of information will be much easier than interpreting a display of many bits of information. Also affecting glaceability are design elements such as color, shape, position, size, and contrast, which are used to represent information in a variety of ways.
% Would be helpful for secondary information [DEFINE secondary info]. To avoid the user needing to remember in which direction the information was placed, this information could be anchored by representative icons. Or the primary information which hides related information (e.g. task list that shows current and a limited amount of next steps, that displays the complete list when accessed)

% HUD BEHAVIOR
Instead of showing the interface at all times, its elements could be positioned outside of the HMD's field of view, accessible by turning the head in that direction. This is the core idea of "Glanceable AR".

\textcite{luGlanceableAREvaluating2020} proposes two concepts to achieve this, comparing it with a typical 2D HUD.

\textbf{Head-Glance.} Interface components are placed just outside the display's field of view and are accessed turning the head. This approach requires an additional sensor for the position of the body, so the head movement can be tracked in relation to the body.

\textbf{Gaze-Summon.} Here, anchors are placed near the position of where the elements would be placed. If this point is fixated for a certain amount of time, the information will appear in its stead.



% LU 2020, 2023
% - "designing glanceable interfaces requires careful consideration not only about how to present information visually, but also about how to access the information effectively"
% \textcite{luGlanceableAREvaluating2020} proposes four design principles: "DP1. Virtual content should be fixed to the user. DP2. Virtual content should be spatially distributed in the periphery. DP3. The interaction to access virtual content should be hands-free. DP4. Information should be accessed by glancing quickly at the periphery."
% - voice input: disturbs others in public, HERE: radio comms, loud industrial env
% - "we define “periphery” as the space at the edges of or beyond the field of view (FoV) of the AR display"
% - eye-glance interface (HUD)
% 	- baseline, does not require sensors or trackers
% 	- "benefits of information being highly visible and accessible, but it may also be obtrusive, occlude the real world, and cause the problem of information overload"
% 	- always-there information might interfere with peripheral awareness
% - head-glance
% 	- content outside FOV, fixed to body, turn head to access -> clear view
% 	- requires to look away from forward FOV momentarily, impacted performance of primary task in study (keeping a specified distance to virtual human when walking)
% 		- HYPO might be problematic when moving quickly (emergency)
% 	- mental demand higher in study, possibly because of
% 		- frequency of information access, leading to a lot of extra head movement avoidable by other methods
% 		- need to remember location of information
% - gaze-summon (look at indicator for 0.5 sec to display information)
% 	- additional time needed to access information results in unusability for industrial use case
% 	- possible eye strain from keeping gaze on target
% 	- increase of false positives when participants took a turn (reflex to look into intended direction + eye-tracking jitter from quick head movements)
% \textcite{luGlanceableAREvaluating2020} mentions the display being less impactful when participants concentrated on the primary task. CONCENTRATION LEVEL?
% - CON primary task of walking not comparable to task with high cognitive load + physical demands

% \textcite{ishiguroPeripheralVisionAnnotation2011} presented a method to show a simple icon that transitions to related information when gazed at.

% **passive/ambient/top-down**
% By default, the display just shows necessary information. This mode is designed to not get the user's attention so they can focus on their primary task. Another reason to avoid color and movement here is to have the maximum contrast possible if the user needs to get notified of something.

% INTERRUPTION
% - "Design variables used for capturing user attention include abrupt onset, flashing, bouncing, and other motion." \cite{matthewsDefiningDesigningEvaluating2005}
% Notification levels equal importance of information, corresponding to action priority (in HUD case)
% TABLE notification level and corresponding design choices + elements
% e.g. change blind, make aware, interrupt, demand action x size, location, color, motion (+ frequency),...

% **interruption/active/notification/bottom-up/**
% \cite{janakaNotiFadeMinimizingOHMD2023} getting attention without harshly interrupting primary task
% \cite{salisburyAttentionChangesHeadWorn2024}
% \cite{chewarUnpackingCriticalParameters2004} IRC framework (interruption, reaction, comprehension)

This further ties into context-aware interfaces, which display information based on current task or cognitive load \cite{rhodesWIMPInterfaceConsidered1998}. The risk of false positives is unjustifiable in safety-critical environments.
% context awareness \cite{krevelenSurveyAugmentedReality2010}