\section{Conceptualization}

\subsection{Data Visualisation}

weighting of parameters if space is limited, visual hierarchy

GRAPHIC modes of information ordered by parsing time
e.g. color, movement, iconography, text

general principles regardless of medium, modify w/ findings from previous sections

How fast are certain types of data visualisation parsed, considering cognitive load?

effects of color? monochrome? w/ accents?

unnatural colors might give good contrast, but cause eye strain over time

would be interesting to see if certain colors would have a calming effect, thus saving oxygen or sth

diagrams vs just a number? mainly number, diagram in special cases like oxygen use

show units? Y, except low on space/minimal version

movement

pop up warning

icons vs unit
unit format -> might be less relevant if number + smaller unit
- more relevant when testing if goal is least mental load

Iconography

Typography

avoid light font weights

traffic light system

language?

just icons for hazardous atmosphere/environment

\subsection{User Interface}

ELEMENTS

requirements: lowest mental/sensory load possible

Diagrams vs just a number (movement of diagram might be distracting)

2 full examples: full/more detailed on CPC glass, minimal version on goggles

each on dark + varied bg

LAYOUT

positioning elements? some directions seem to be favored for distractability?

FOV diagram w/ angles

do i need to leave space at the sides for peripheral vision? how much?

---

2 layers: main info (HUD, doesn't move) + AR (hazard highlighting, moves)

overlap? "border" where highlights disappear before overlapping w/ HUD?
