\section{Potential Usage Scenarios}

Confined Space Entry, Emergency Response, Cleanrooms, Diving (+ water pressure, depth)

Apart from chemical protective clothing, a HMD is useful combined with any equipment that limits FOV and/or mobility.

All of these scenarios involve a certain level of danger or hazards, making it imperative to not cut off senses if system breaks -> optical see-through (see section tech)

Further, the work conditions are characterized by a high mental load. A goal of the HUD would also be to lighten this load, although the types of information needed to do that would differ, e.g. for cleanrooms it might be more useful to include a protocol or list of steps. Since this is a controlled environment there are no unexpected hazards or events, no need for watching critical parameters. 

For an overview of properties relevant for HUD UI design, reference table X.

heart rate

% will get big enough to put in appendix
\begin{table}[hb]
\begin{tabular}{l | p{0.25\linewidth} | p{0.25\linewidth} | p{0.25\linewidth}}
 & Confined Spaces & Emergency Response & Cleanrooms \\
 \hline
 Lighting & dark & varied & bright \\
 Background & simple & dynamic & simple? \\
 Common Hazards &  &  & \\
 Relevant Information &  Oxygen, Indicators for Heat Exhaustion, Hazard Warnings & same as Confined Spaces + more complex information (team status, navigation,...) & Task List \\
\end{tabular}
\end{table}

\section{Biological and Psychological Requirements}

mitigating autopilot mode for routine tasks

cognitive load

\subsection{Human Vision}

vision + focus distance

eye FOV diagram

eye strain with light-emitting displays
does that get worse if the display is closer to the eye?
is eye strain linked to earlier exhaustion?

ui design possibilities to reduce eye strain
trade-offs: low contrast vs visibility

how does acute stress/panic affect vision? what about physical emergencies, like dizziness? fov narrower? vision loss? blur?

\subsection{Perceptual Psychology}

reaction to color + movement

\subsection{Psychological Safety}

\section{Current Technological Limitations}

What are common drawbacks of all possible technologies that might be mitigated via UI design?

Display-Größe, Anordnung
Helm/Atemmaske vs Schutzanzug

o diagram side view CPC
distance of helmet/CPC visor to face

\subsection{Optical See-Through Display/Holographic Image}

functionality

image formed through light
additive color model

lighter color = more light + opacity
EYE strain

\subsection{Lighting Conditions}

\subsection{Background Variation}

50-70\% transparency in brightly-lit room \parencite{hussainEffectTransparencyLevels2024}

Since Confined Spaces have minimal lighting (see section 1), they are an optimal background for readability. The brightness and opacity should be reduced.

dark env + torch: harsh lighting makes difference?

2 layers: main info (HUD, doesn't move) + AR (hazard highlighting, moves)

overlap? "border" where highlights disappear before overlapping w/ HUD?

\subsection{Movement Tracking}

only include if relevant to final UI designs

\section{Conceptualization}

\subsection{Data Visualisation}

general principles regardless of medium, modify w/ findings from previous sections

How fast are certain types of data visualisation parsed, considering cognitive load?

effects of color? monochrome? w/ accents?

unnatural colors might give good contrast, but cause eye strain over time

would be interesting to see if certain colors would have a calming effect, thus saving oxygen or sth

diagrams vs just a number? mainly number, diagram in special cases like oxygen use

show units? Y, except low on space/minimal version

movement

pop up warning

iconography

traffic light system

language?

just icons for hazardous atmosphere/environment

\subsection{User Interface}

ELEMENTS

requirements: lowest mental/sensory load possible

Diagrams vs just a number (movement of diagram might be distracting)

2 full examples: full/more detailed on CPC glass, minimal version on goggles

each on dark + varied bg

LAYOUT

positioning elements? some directions seem to be favored for distractability?

FOV diagram w/ angles

do i need to leave space at the sides for peripheral vision? how much?


\section{Visual Prototype}

Ideally, the finished system shows as much information as possible/necessary without limiting situational awareness or causing fatigue and sensory overload.

properties of used hardware (probably MetaQuest 3)

video see-through, video feed/encoding may falsify colors + contrast in comparison to complex real-life lighting conditions.

development process

\subsection{Creating a Dummy Dataset}

- oxygen supply

solution to detect dangerous levels of exhaustion early
- heart rate + variability
- body temperature
- blood pressure?
- breathing
- activity intensity




\section{outlook}

augmenting other senses e.g. noise sources when hearing protection is worn?
