\section{Data Visualization}
\label{sec:datavis}

Visualizating data transforms it into information. Data itself is just noise, whereas information holds value. In what way data needs to be transformed is determined by context [\cite{terganKnowledgeInformationVisualization2005}].

The type of visualization depends on the purpose of the information. The main constraint in this case is cognitively demanding situations.

\subsection{Situation Awareness and Cognitive Load}

As mentioned earlier, the tasks to execute are mentally demanding. Concentrating on fulfilling task objectives while maintaining awareness of the surrounding area result in a high cognitive load, while associated risks prohibit human error. Endsley's model of situation awareness can be referenced to estimate the requirements of information acquisition in dynamic situations.

\textcite{endsleyTheorySituationAwareness1995} proposes a model of situation awarenes, describing the process of decision-making in dynamic situations. This includes 3 levels, namely perception, comprehension and projection. Only Level 1 awareness—perception—is relevant for UI design itself, though some concepts from Level 2 can be used to exemplify things to avoid.

By displaying relevant information on a HUD, some level of situational awareness could be restored. Freeing up cognitive load, which can then be reallocated. Going by Endsley's definition, that would increase the likelihood of making better decisions.

- "role of goals and goal-directed processing in directing attention and interpreting the significance of perceived information"
- circles back to visual attention
    - goal-directed (top-down) vs data-directed (bottom-up) processing
	- information salience to grab attention (data-driven)
- "people as active participants in the development of their own SA, based on how they direct their attention, communicate with team mates, and manipulate their tools to search for desired information"
- "ongoing dynamic process of gathering and interpreting information to update the situation model and using that situation model to search for information until decisions can be made"

- "role of environmental, task, and system factors in SA, including the capability of systems for deriving needed information; the effect of system complexity on SA; the **effectiveness of the user interface for providing rapid access and understandability of needed information**; the role of stressors, workload, and fatigue on SA mechanisms and processes; and the effect of automation on SA"
ENDSLEY 1995 mentions the advantage of systems providing processed information instead of only the data it is based on (i.e. displaying remaining time based on current oxygen amount and usage). Other recommendations are:
- focus types and grouping of information on supporting decision-making for current goal (-> context awareness)

"Cognitive load theory (CLT) is concerned with the design of interfaces that allow users maximize their working memory when problem solving. This includes eliminating any subjective mental load that may be imposed by the instruction interface." DABOR 2019 SIMULT INTERPRETATION

\subsection{Types of Information}

Depending on the character of the data, different methods of visualization could be chosen.

Comparable to basic dashboard data, only value of the parameter is relevant, since there is no relationship between the data. At most it is the relation between a current and a past value of a parameter.

Purposes of color to cenvey information are grouping or relationships. Grouping is necessary for the HUD, but is managed by the spatial location of and the spacing between elements.

\cite{wilke2VisualizingData2019}
https://learning.oreilly.com/library/view/fundamentals-of-data/9781492031079/ch02.html

\subsection{Visualization Methods}